### 2018-05-01 Documents/bootcamp_project_turnin.tex
turn in instructions

\textbf{Due Date: Midnight, at the end of the day December 21st}

@@

All of this must be done prior to midnight, at the end of the day December 21st. Finally, \textbf{do not modify} your work after the 21st until you have received grade from me. After you have received a grade, you may treat the project as yours as continue to work on it as you like.

@@

This project was completed by \textbf{insert full name here} in partial fulfilment of  ECON-UB.0232, Data Bootcamp, Fall 2017. I certify that the NYU Stern Honor Code applies to this project. In particular, I have:

>>>>

\textbf{Due Date: Midnight, May 14, 2018}

@@

All of this must be done prior to midnight, at the end of the day May 14. Finally, \textbf{do not modify} your work after the 14th until you have received grade from me. After you have received a grade, you may treat the project as yours as continue to work on it as you like.

@@

This project was completed by \textbf{insert full name here} in partial fulfilment of  ECON-UB.0232, Data Bootcamp, Spring 2018. I certify that the NYU Stern Honor Code applies to this project. In particular, I have:
